### 2012-11-27 inst/examples/multiple_uncertainty.Rmd

``` {r }
xmin <- 0
xmax <- 200
grid_n <- 40
````

@@

```{r }
sdp_g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .5, pdfn, 0, 0)
sdp_m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, .5, 0)
sdp_i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, .5)
opt_g <- find_dp_optim(sdp_g, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_m <- find_dp_optim(sdp_m, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_i <- find_dp_optim(sdp_i, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
XMAX <- 140
policy <- melt(data.frame(stock = x_grid, deterministic=det$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))

dat <- subset(policy, stock < XMAX)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	geom_jitter(aes(x,y, color=variable), shpae='+') +
  xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```

>>>>

``` {r }
xmin <- 0
xmax <- 200
grid_n <- 200
````

@@

```{r }
sdp_low <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .1, pdfn, 0, 0)
sdp_g <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, .5, pdfn, 0, 0)
sdp_m <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, .5, 0)
sdp_i <- SDP_multiple_uncertainty(f, pars, x_grid, h_grid, 0, pdfn, 0, .5)
opt_low <- find_dp_optim(sdp_low, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_g <- find_dp_optim(sdp_g, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_m <- find_dp_optim(sdp_m, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
opt_i <- find_dp_optim(sdp_i, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
```

@@

``` {r sethiplots, cache=FALSE}
require(reshape2)
XMAX <- 140
policy <- melt(data.frame(stock = x_grid, det=det$D[,1], low_g = opt_low$D[,1], growth = opt_g$D[,1], meas = opt_m$D[,1], imp = opt_i$D[,1]), id = "stock")
ggplot(subset(policy, stock < XMAX)) + geom_jitter(aes(stock, stock-x_grid[value], color=variable))

dat <- subset(policy, stock < XMAX)
dt <- data.table(dat)
linear <- dt[,approx(stock, stock-x_grid[value], xout=seq(1,XMAX, length=15)), by=variable]
ggplot(linear) + 
	stat_smooth(aes(x,y,color=variable), degree=1, se=FALSE, span=.3) + 
	geom_jitter(aes(x,y, color=variable), shape='+') +
  xlab("Measured Stock") + ylab("Optimal Expected Escapement")
```
